\huge Tor's Usability for Censorship Circumvention

### 2016-05-10 pets2017-paper/pets2017-paper.tex
put appendixes in order.

After participants completed the browsing tasks or ran out of time,
we interviewed them about their experience and
took notes of the questions and answers.
We asked three standard questions asking about their general experience, 
interface features they found confusing, and feedback for improvements. We followed up
with specific questions prompted from watching their screen. 
This was to verify any hypotheses we had (e.g. ``they did not know what an ISP was'').
We paid each participant~\$30 for their time.

@@

\subsubsection{Rate of Success} 
49 of 56 (88\%) participants with the new interface successfully connected to Tor, while 45 of 58 (78\%) participants with the old interface did. 
Due to the limited number of participants, this difference is not large enough to rule out the possibility of random chance being the cause for the difference. This suggests that users no less likely to succeed with the new interface. 
% impact of version on success: not significant (Mann--Whitney $W = 5.5$, $p = 0.8248$)
%impact of env on success: not significant (Kruskal--Wallis $\chi^2 = 4.7059$, $\mbox{df} = 2$, $p = 0.09509$)

@@

Only two participants chose to configure a custom bridge. Both of these participants sent an incorrectly formatted request to the automatic bridge responder, which did not reply with custom bridges as a result. Appendix~\ref{failed-participants} shows the malformed requests. These two participants failed to connect to the Tor network.

@@

\item {\bfseries Used the bridges auto-responder incorrectly (2/19).} P94, P109, who were in E3, emailed the bridges auto-responder to get custom bridges. However, they formatted the message incorrectly and thus failed to get a response (Appendix~\ref{failed-participants}).
\end{description}

@@

\appendix
\section{Participant Worksheet Text} 
\label{participant-worksheet}
Imagine you live in an oppressive country that censors part of the Internet. We have simulated this in the laboratory by blocking certain websites and services. The purpose of this experiment is to evaluate the use of Tor browser, which is a browser that can circumvent censorship and let you visit blocked websites. For instance, www.torproject.org is blocked. Check this by going to the site on a standard browser, like Firefox, Chrome, or Internet Explorer. It will fail to load, when you can visit other sites.

@@

\section{Post-Experiment Standard Interview Questions}
We asked our participants these questions after they were given time to configure Tor Browser. \\

@@

\section{Statistical Tests} 
From our measurements, we observe that participants with the new interface 
have a higher rate of success, succeed in less time, and configure their interface in less time. 
We do not find that the increased rate of success with the new interface or the decreased time to success with the new interface significant. That is, random chance can account for the difference. 
We do find the the decreased active configuration time to be significant. 
We describe the methodology for the statistical tests used in this paper to determine the impact of the interface on success rate, time to success, and active time.

@@

\section{Custom Bridge Attempts} 
\label{failed-participants}

>>>>

After participants completed the browsing tasks or ran out of time,
we interviewed them about their experience and
took notes of the questions and answers.
We asked questions asking about their general experience, 
interface features they found confusing, and feedback for improvements (Appendix~\ref{interview-questions}). 
We followed up with specific questions prompted from watching their screen. 
This was to verify any hypotheses we had (e.g. ``they did not know what an ISP was'').
We paid each participant~\$30 for their time.

@@

\subsubsection{Rate of Success} 
49 of 56 (88\%) participants with the new interface successfully connected to Tor, while 45 of 58 (78\%) participants with the old interface did. Due to the limited number of participants, this difference is not large enough to rule out the possibility of random chance being the cause for the difference. Appendix~\ref{stat-tests} details the methodology for the statistical tests used in this paper.

@@

Only two participants chose to configure a custom bridge. Both of these participants sent an incorrectly formatted request to the automatic bridge responder, which did not reply with custom bridges as a result. Appendix~\ref{custom} shows the malformed requests. These two participants failed to connect to the Tor network.

@@

\item {\bfseries Used the bridges auto-responder incorrectly (2/19).} P94, P109, who were in E3, emailed the bridges auto-responder to get custom bridges. However, they formatted the message incorrectly and thus failed to get a response (Appendix~\ref{custom}).
\end{description}

@@

\appendix

@@

\section{Participant Worksheet Text} 
\label{participant-worksheet}
Imagine you live in an oppressive country that censors part of the Internet. We have simulated this in the laboratory by blocking certain websites and services. The purpose of this experiment is to evaluate the use of Tor browser, which is a browser that can circumvent censorship and let you visit blocked websites. For instance, www.torproject.org is blocked. Check this by going to the site on a standard browser, like Firefox, Chrome, or Internet Explorer. It will fail to load, when you can visit other sites.

\section{Post-Experiment Standard Interview Questions}
\label{interview-questions}
We asked our participants these questions after they were given time to configure Tor Browser. \\

@@

\section{Statistical Tests} 
\label{stat-tests}
From our measurements, we observe that participants with the new interface 
have a higher rate of success, succeed in less time, and configure their interface in less time. 
We do not find that the increased rate of success with the new interface or the decreased time to success with the new interface significant. That is, random chance can account for the difference. 
We do find the the decreased active configuration time to be significant. 
We describe the methodology for the statistical tests used in this paper to determine the impact of the interface on success rate, time to success, and active time.

@@

\section{Custom Bridge Attempts} 
\label{custom}
